dyngen: a multi-modal simulator for spearheading new single-cell omics analyses

### 2021-05-12 manuscript/manuscript.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  table,
  10pt,
  a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={dyngen: a multi-modal simulator for spearheading new single-cell omics analyses},
  pdfauthor={Robrecht Cannoodt,1,2,3; Wouter Saelens,1,2; Louise Deconinck1,2; Yvan Saeys1,2,},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{tcolorbox}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{fontspec}
\usepackage{pifont}
\usepackage{float}
\usepackage{caption}
\captionsetup[table]{position=bottom}
\setmainfont [Path = fonts/,
  UprightFont = *-300,
  ItalicFont = *-300-Italic,
  BoldFont = *-700,
  BoldItalicFont = *-700-Italic
]{MuseoSans}

\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[sorting=none,url=false,backend=bibtex]{biblatex}

\usepackage{filecontents}

\bibliography{\jobname}

\title{dyngen: a multi-modal simulator for spearheading new single-cell
omics analyses}
\author{Robrecht Cannoodt\textsuperscript{$\dagger{}$,1,2,3} \and Wouter
Saelens\textsuperscript{$\dagger{}$,1,2} \and Louise
Deconinck\textsuperscript{1,2} \and Yvan Saeys\textsuperscript{1,2,*}}
\date{12 May 2021}

@@

\textsuperscript{1} Data Mining and Modelling for Biomedicine group, VIB
Center for Inflammation Research, Ghent, Belgium\\
\textsuperscript{2} Department of Applied Mathematics, Computer Science,
and Statistics, Ghent University, Ghent, Belgium\\
\textsuperscript{3} Data Intuitive, Lebbeke, Belgium

@@

\begin{filecontents}{\jobname.bib}
@Article{aibar_scenicsinglecellregulatory_2017,
	title = {{{SCENIC}}: Single-Cell Regulatory Network Inference and Clustering},
	author = {Sara Aibar and Carmen Bravo Gonz{\a'a}lez-Blas and Thomas Moerman and V{\^a}n Anh Huynh-Thu and Hana Imrichova and Gert Hulselmans and Florian Rambow and Jean-Christophe Marine and Pierre Geurts and Jan Aerts and Joost {van den Oord} and Zeynep Kalender Atak and Jasper Wouters and Stein Aerts},
	year = {2017},
	month = {oct},
	issn = {1548-7091},
	doi = {10.1038/nmeth.4463},
	journal = {Nature Methods},
}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  table,
  10pt,
  a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={dyngen: a multi-modal simulator for spearheading new single-cell omics analyses},
  pdfauthor={Robrecht Cannoodt,1,2,3; Wouter Saelens,1,2,4; Louise Deconinck1,2; Yvan Saeys1,2,},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{tcolorbox}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{fontspec}
\usepackage{pifont}
\usepackage{float}
\usepackage{caption}
\captionsetup[table]{position=bottom}
\setmainfont [Path = fonts/,
  UprightFont = *-300,
  ItalicFont = *-300-Italic,
  BoldFont = *-700,
  BoldItalicFont = *-700-Italic
]{MuseoSans}

\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[sorting=none,url=false,backend=bibtex]{biblatex}
\addbibresource{\jobname.bib}
\begin{filecontents}{\jobname.bib}
@Article{aibar_scenicsinglecellregulatory_2017,
  title = {{{SCENIC}}: Single-Cell Regulatory Network Inference and Clustering},
  author = {Sara Aibar and Carmen Bravo Gonz{\a'a}lez-Blas and Thomas Moerman and V{\^a}n Anh Huynh-Thu and Hana Imrichova and Gert Hulselmans and Florian Rambow and Jean-Christophe Marine and Pierre Geurts and Jan Aerts and Joost {van den Oord} and Zeynep Kalender Atak and Jasper Wouters and Stein Aerts},
  year = {2017},
  month = {oct},
  issn = {1548-7091},
  doi = {10.1038/nmeth.4463},
  journal = {Nature Methods},
}

@Article{lizio_gatewaysfantom5promoter_2015,
  title = {Gateways to the {{FANTOM5}} Promoter Level Mammalian Expression Atlas},
  author = {Marina Lizio and Jayson Harshbarger and Hisashi Shimoji and Jessica Severin and Takeya Kasukawa and Serkan Sahin and Imad Abugessaisa and Shiro Fukuda and Fumi Hori and Sachi Ishikawa-Kato and Christopher J. Mungall and Erik Arner and J. Kenneth Baillie and Nicolas Bertin and Hidemasa Bono and Michiel {de Hoon} and Alexander D. Diehl and Emmanuel Dimont and Tom C. Freeman and Kaori Fujieda and Winston Hide and Rajaram Kaliyaperumal and Toshiaki Katayama and Timo Lassmann and Terrence F. Meehan and Koro Nishikata and Hiromasa Ono and Michael Rehli and Albin Sandelin and Erik A. Schultes and Peter AC {`t Hoen} and Zuotian Tatum and Mark Thompson and Tetsuro Toyoda and Derek W. Wright and Carsten O. Daub and Masayoshi Itoh and Piero Carninci and Yoshihide Hayashizaki and Alistair RR Forrest and Hideya Kawaji and {the FANTOM consortium}},
  year = {2015},
  month = {jan},
  volume = {16},
  pages = {22},
  issn = {1465-6906},
  doi = {10.1186/s13059-014-0560-6},
  abstract = {The FANTOM5 project investigates transcription initiation activities in more than 1,000 human and mouse primary cells, cell lines and tissues using CAGE. Based on manual curation of sample information and development of an ontology for sample classification, we assemble the resulting data into a centralized data resource (http://fantom.gsc.riken.jp/5/). This resource contains web-based tools and data-access points for the research community to search and extract data related to samples, genes, promoter activities, transcription factors and enhancers across the FANTOM5 atlas.},
  journal = {Genome Biology},
  number = {1},
}

\title{dyngen: a multi-modal simulator for spearheading new single-cell
omics analyses}
\author{Robrecht Cannoodt\textsuperscript{$\dagger{}$,1,2,3} \and Wouter
Saelens\textsuperscript{$\dagger{}$,1,2,4} \and Louise
Deconinck\textsuperscript{1,2} \and Yvan Saeys\textsuperscript{1,2,*}}
\date{12 May 2021}

@@

\textsuperscript{1} Data Mining and Modelling for Biomedicine group, VIB
Center for Inflammation Research, Ghent, Belgium\\
\textsuperscript{2} Department of Applied Mathematics, Computer Science,
and Statistics, Ghent University, Ghent, Belgium\\
\textsuperscript{3} Data Intuitive, Lebbeke, Belgium\\
\textsuperscript{4} Institute of Bioengineering, School of Life
Sciences, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne,
Switzerland

@@
